$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-05 paper/paper.tex
Rephrase subject reduction

\todo{intro}
\todo{I wonder if we can remove the proofs everywhere and comment on them in the intro and where they can be found.}

@@

In the linear \picalc{} reduction affects the usage context: communicating over a channel takes away $\one$ input and $\one$ output multiplicity.

\begin{nitheorem}[Subject reduction]
  Let $P \reduce{c} Q$.
  If $c$ is $\constr{internal}$, then $\Gamma' \equiv \Gamma$.
  If however $c$ is $\constr{external}\; i$, then $\containsusage{\Gamma'}{i}{\lio}{\Gamma}$.
  Given $\types{\gamma}{\Gamma'}{P}{\Xi}$ then after reduction $\types{\gamma}{\Gamma}{Q}{\Xi}$.
\end{nitheorem}

\begin{proof}
  \hfill{}\\
  \begin{itemize}
    \item
    In the $\constr{comm}$ case we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).

>>>>

\todo{intro}

@@

\begin{nidefinition}
  For convenience, we use $\containsusage{\Gamma}{i}{x}{\Delta}$ to stand for $\contains{\gamma}{\Gamma}{i}{t}{x}{\Delta}$ for some $\gamma$ and $t$.
\end{nidefinition}

\begin{nitheorem}[Subject reduction]
  If $P$ reduces to $Q$ and $P$ is well-typed, then so is $Q$.
  In the \picalc{} we distinguish between a reduction $P \reduce{\constr{internal}} Q$ by communication on a channel created within $P$, and a reduction $P \reduce{\constr{external} \; i} Q$ by communication on a channel created outside of $P$.
  \begin{itemize}
    \item If the reduction is internal, we prove that if $\types{\gamma}{\Gamma}{P}{\Xi}$ then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
    \item If the reduction is external and on channel $i$, we prove that if $\types{\gamma}{\Gamma'}{P}{\Xi}$ and $\containsusage{\Gamma'}{i}{\lio}{\Gamma}$ , then $\types{\gamma}{\Gamma}{Q}{\Xi}$.
  \end{itemize}
\end{nitheorem}

\begin{proof}
  By induction on the typing derivation on $P$.
  \hfill{}\\
  \begin{itemize}
    \item
    In the $\constr{comm}$ case we apply framing (\autoref{thm:framing}) to rearrange the assumptions and then apply substitution (\autoref{thm:substitution}) and strengthening (\autoref{thm:strengthening}).
